Northern Pikeminnow Abundance in Deadwater Slough, Salmon River, Idaho, and Potential Impacts to Local Chinook Salmon Populations

### 2022-04-07 analysis/paper/paper.Rmd
updated BibTex library

The Deadwater Slough is an approximately `r round(ddw_rkms, 1)` km section of the mainstem Salmon River located roughly 6 river kilometers (rkm) downstream from the town of North Fork, Idaho (Figure \@ref(fig:map)). The downstream end of the slough is located at the confluence of Dump Creek and the Salmon River. A large alluvial fan at the mouth of Dump Creek has, at least partially, created a hydraulic control in the Salmon River resulting in the formation of Deadwater Slough. Although the origin and timing of the alluvial fan and Deadwater Slough is somewhat ambiguous [@Reichmuth1958; @USACE1986], they likely coincided with the failure of a small mining reservoir in the Dump Creek drainage around 1897 that deposited substantial amounts of sediment at its confluence with the Salmon River [@Emerson1973]. The slough is currently a slow, deep section in the river, spanning approximately `r round(ddw_hectares)` hectares, averaging `r round(ddw_avg_width_m)` m wide, and has characteristics resembling a small reservoir.

>>>>

The Deadwater Slough is an approximately `r round(ddw_rkms, 1)` km section of the mainstem Salmon River located roughly 6 river kilometers (rkm) downstream from the town of North Fork, Idaho (Figure \@ref(fig:map)). The downstream end of the slough is located at the confluence of Dump Creek and the Salmon River. A large alluvial fan at the mouth of Dump Creek has, at least partially, created a hydraulic control in the Salmon River resulting in the formation of Deadwater Slough. Although the origin and timing of the alluvial fan and Deadwater Slough is somewhat ambiguous [@Reichmuth1985; @USACE1986], they likely coincided with the failure of a small mining reservoir in the Dump Creek drainage around 1897 that deposited substantial amounts of sediment at its confluence with the Salmon River [@Emerson1973]. The slough is currently a slow, deep section in the river, spanning approximately `r round(ddw_hectares)` hectares, averaging `r round(ddw_avg_width_m)` m wide, and has characteristics resembling a small reservoir.
